Stay in shape! Homework exam II

### 2016-04-02 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
finsihed RIC algorithm
started with the analises
finished e and f

\begin{algorithmic}[1]
	\Function{calulateBiggestDisk}{$H$}
		\State
		$d_0 \gets arbitrarlyLargeDisk()$
		\If{hasArbitrarlylargeDisc($H$)}
			\State
			\Return $d_0$
		\EndIf
		\State
		$H_r \gets$ random shuffle $H$
		\For{$i\gets 1$ to $n$ with $h_i \in H_r$}
			\State
			$d_i \gets d_{i-1}$
			\If{$d_{i-1} \not\subset h_i$}
			\State
			$d_i \gets createLargestDiskFrom(h_i, \{h_0\dots,h_{i-1}\})$
			\EndIf
		\EndFor
	\EndFunction
\end{algorithmic}

\subsection{Prove the expected running time}
% Don't forget to remove constants

\subsection{Eplain why you can't use RIC for points}
\section{A datastructure for horizontal line segments}

>>>>

\begin{algorithmic}[1]
	\Function{calculateBiggestDisk}{$H$}
		\State
		$d_0 \gets arbitrarlyLargeDisk()$
		\If{hasArbitrarlylargeDisc($H$)}
			\State
			\Return $d_0$
		\EndIf
		\State
		$H_r \gets$ random shuffle $H$
		\For{$i\gets 1$ to $n$ with $h_i \in H_r$}
			\State
			$d_i \gets d_{i-1}$
			\If{$d_{i-1} \not\subset h_i$}
			\State
			$d_i \gets calculateBiggestDiskFrom(h_i, \{h_0\dots,h_{i-1}\})$
			\If{$d_i = None$}
				\State
				\Return $None$
			\EndIf
			\EndIf
		\EndFor
		\State
		\Return $d_n$
	\EndFunction
	\Function{calculateBiggestDiskFrom}{$h_{bound}$,$H_{prev}$}
		\State
		$d_0 \gets arbitrarlyLargeDisk()$
		\For{$i\gets 1$ to $n$ with $h_i \in H_{prev}$}
			\State
			$d_i \gets d_{i-1}$
			\If{$h_i$ does not point in the same direction as $h_{bound}$}
			\If{$d_{i-1} \not\subset h_i$}
				\If{$h_i \cap h_{bound}$ does not intersect the x-axis}
					\State
					\Return $None$
				\EndIf
				\If{$h_i$ is parralel to the x axis}
				\State
				%TODO, the calculation with math?
				$d_i \gets$ Calculate the leftmost largest disk in $h_{bound} \cap h_{i}$
				\Else
				\State
				$d_i \gets$ Calculate the largest disk in $h_{bound} \cap h_{i}$
				\EndIf
				\State
			\EndIf
			\EndIf
		\EndFor
		\State
		\Return $d_n$
	\EndFunction
\end{algorithmic}

\subsection{Prove the expected running time}
It should be noted that both $calculateBiggestDisk(H)$ and
$calculateBiggestDiskFrom(h,H)$ are both linear time functions.
And so worst case $calculateBiggestDisk(H)$ is worst case:

\[O(n^2)\]

% Don't forget to remove constants
We will prove that a$calculateBiggestDisk(H)$ will run in $\Theta(n)$ expected
time with help of backwards analises: Consider the situation after $h_i$ is
inserted, and $d_i$ is computed (either by $d_i = d_{i-1}$ or with help
of $calculateBiggestDiskFrom(h_i,H)$). If $h_i$ does not bound the feasible
region, or $d_i \subset h_i$, then the addition step was cheap
and took $\Theta(1)$ time. But if $d_i \not\subset h_i$ then the addition
step was expensive.

There are $i$ half-planes that could have been defining $d_i$, and $i-2$
of these are in random order. Since the order was reandom eacho of the $i-2$
half-planes has the same probability to be the last one added, and only
$\leq$ 2 of these cause the expensive step.

Excpected time for $i$-th addition:

\[\frac{i-4}{i-2}\cdot\Theta(1)+\frac{2}{i-2}\cdot\Theta(i)=\Theta(1)\]

Total expected running time:

\[3\Theta(n) = \Theta(n)\]

\subsection{Eplain why you can't use RIC for points}
To create a RIC algorithm with linear expected time we need to have the
following properties, lets go trough each of one to see if they get violated.

\begin{itemize}
	\item \emph{The test wether the next input object violates the current
		optimum must be possible and fast.}
		This is true for this problem. Checking if a point is inside a disk
		is trivially easy.
	\item \emph{If the next input boject violates the current optimum,
		finding the new optimum must be an easier problem than the general
		problem.}
		This is the violating property. because you can still move
		the disk having a point violate the current disk may not be a point
		wich with the disks boundary has to intersect.

		A more crude way to put it is that you can have multiple optimum
		that don't intersect the same points.
	\item \emph{The optimum must already be defined by O(1) of the input
		objects.}
		I think this is true, you can use some math to figure out a new
		optimum.
	\item \emph{The analysis must work out.}
		It doesn't work out because you can't gaurantee that you've just
		found a local optimum instead of a global optimum. I mean you
		could use this as a heuristic but not as an anwser.
\end{itemize}
\section{A datastructure for horizontal line segments}
